---
title: "tmp"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("json_unpack_fxns.R")
library(rjson)
library(RCurl)
library(data.table)

# smallest file: "data/full zendesk 042020.json"

filepath <- "data/full zendesk 092020.json"

data <- rjson::fromJSON(sprintf("[%s]", 
                                paste(readLines(filepath),collapse=",")))
```

note - "full zendesk 012821.json" has more than 2^31-1 bytes and exceeds C's 
memory limit, which is what the fromJSON fxn is implemented in.

goal is to sort this into a 2 column dataframe: ticketID & comments

First, let's sort the first item into ticketID and comments

access token: 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

```{r}
item <- data[[1]]

# well, id is easy enough to grab

id <- item$id
comments <- item$comments
```

Sample code for extracting ID and Comments

```{r}
filepath <- "data/full zendesk 042020.json"

data <- load_data(filepath)
data <- construct_comments_data_frame(data)

write.csv(data, "veros_output.csv", row.names = TRUE)
```

Vero's export:

```{r}
source("json_unpack_fxns.R")
load_libraries()

filepath <- "data/veros_export.json"

data <- load_data(filepath)
data <- construct_comments_data_frame(data)

data.table::fwrite(data, "data/outputs/veros_output.csv")
```

Exploring adding filtering by customer

```{r}
# only get US Cellular data
source("json_unpack_fxns.R")
load_libraries()

filepath <- "data/veros_export.json"

data <- load_data(filepath)
data <- construct_comments_org_data_frame(data)
data <- data[data$org == "US Cellular", ]

data.table::fwrite(data, "data/outputs/veros_output_v2.csv")

```

```{r}
source("json_unpack_fxns.R")
load_libraries()

filepath <- "data/parser_input/export-2022-02-01.json"

data <- load_data(filepath)
data <- construct_comments_org_data_frame(data)
data <- data[data$org == "US Cellular", ]

data.table::fwrite(data, "data/outputs/zendesk_outputs_2022-02-01.csv")
```

